\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
comment on causality

% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
Since partial correlation is a symmetric measure, the causal mechanism behind the
interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
be directly inferred\footnote{Also note that two other causal mechanisms might be
implied while having a non-zero partial coefficient: (i) a pair of variables
is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
\cite{de2004discovery}.}.
In order to retrieve causal information, we developed an
heuristics based on the following observation. The rise of fluorescence
indicates the activation of a neuron $i$. If a neuron $j$ have also
an increased of fluorescence after a slight delay, this could have been
caused by the neuron $i$. Thus, we count whenever
such events occurred between consecutive time steps
\[
\hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
    \mathbb{1}(x_j^{t+1} - x_i^t \in \left[f_1, f_2 \right]) -
    \mathbb{1}(x_i^{t+1} - x_j^t \in \left[f_1, f_2 \right]), \forall i, j \in V
\]
where $f_1$ and $f_2$ are parameters of the method.
Finally, the weighted average of correlation matrices is combined with $Z$ such
that $Z$ has a contribution of $0.3\%$ to the prediction of an edge.

>>>>

% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
\textcolor{red}{Est-ce qu'on ne le ferait pas passer dans l'appendice B? Ou du moins l'équation?}
Since partial correlation is a symmetric measure, the causal mechanism behind the
interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
be directly inferred\footnote{Also note that two other causal mechanisms might be
implied while having a non-zero partial coefficient: (i) a pair of variables
is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
\cite{de2004discovery}.}.
In order to retrieve causal information, we developed an
heuristics based on the following observation. The rise of fluorescence
indicates the activation of a neuron $i$. If a neuron $j$ have also
an increased of fluorescence after a slight delay, this could have been
caused by the neuron $i$. Thus, we count whenever
such events occurred between consecutive time steps
\[
\hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
    \mathbb{1}(x_j^{t+1} - x_i^t \in \left[f_1, f_2 \right]) -
    \mathbb{1}(x_i^{t+1} - x_j^t \in \left[f_1, f_2 \right]), \forall i, j \in V
\]
where $f_1$ and $f_2$ are parameters of the method.
Finally, the weighted average of correlation matrices is combined with $Z$ such
that $Z$ has a contribution of $0.3\%$ to the prediction of an edge.
